Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-10 paper/paper.qmd
Edits

We use this $R^2$ value to report the effect that corresponds to Cohen’s f guidelines, i.e. $| f |$ is about 0.20 since our $R^2$ falls between the small-medium categories. Even though the statistical test did not yield significant results, this quantity suggests we have approximately a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

This suggests that while our ANOVA results were not statistically significant -- possibly due to insufficient power rather than the absence of any real effect. The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.

@@

Lastly, cognitive retention was measured immediately post-treatment – the long term impacts are not yet explored. To improve our study, we can try to consider individuals with real pain symptoms before the study to ensure a reduction of bias, and provide a realistic test setting. Additionally, carrying the experiment out in the long-term would help with understanding the effects of painkillers and dosages on memory.

@@

Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations -- not all locations were covered equally. This means our findings might not apply to everyone. Next time, we could choose more diverse and evenly spread-out clusters to make the results more general.

@@

This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention. However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects. Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications. This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.

>>>>

We use this $R^2$ value to report the effect that corresponds to Cohen’s f guidelines, i.e. $| f |$ is assumed to be about 0.20 since our $R^2$ falls between the small-medium categories. Even though the statistical test did not yield significant results, this quantity suggests we have approximately a small-medium effect size, indicating that the type of drug and dosage level may still have had a meaningful impact on memory task performance.

@@

This suggests that our ANOVA results were not statistically significant possibly due to insufficient power rather than the absence of any real effect. The observed effect sizes fall into the small range according to Cohen’s conventions, which typically require a larger sample size to detect reliably.

@@

The cognitive retention was measured immediately post-treatment, but the long term impacts are not yet explored. To improve our study, we can try to consider individuals with real pain symptoms before the study to ensure a reduction of bias, and provide a realistic test setting. Additionally, carrying the experiment out in the long-term would help with understanding the effects of painkillers and dosages on memory.

@@

Another issue is that our sample might not fully represent the general population since we selected participants from specific clusters of locations, so not all locations were covered equally. This means our findings might not apply to everyone. Next time, we could choose more diverse and evenly spread-out clusters to make the results more general.

@@

To conclude, this study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention. However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects. Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications. This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
